We organize recommendations by audience.

\subsection{For server maintainers}
\label{sec:rec-server}

\begin{enumerate}
  \item Adopt the Kestrel pump pattern by default. Concretely:
    after \fname{recv()} returns, loop the chunked decoder
    through every chunk available in the read buffer, then deliver
    \emph{one} application-receive event with the concatenated
    data bytes. Cap the per-event delivery by either total bytes
    (a configurable limit, default
    \SI{64}{\kibi\byte}) or time-since-last-flush (configurable,
    default \SI{100}{\milli\second}). Whichever fires first
    triggers the dispatch.
  \item Expose an explicit \fname{streaming} mode for use cases
    that genuinely need byte-by-byte delivery (video uploads,
    long-poll-style hybrids). Make this opt-in.
  \item Add a per-request chunk-count cap with a sensible default
    (e.g., \num{4096} chunks per request) and a configuration
    flag to raise it. This guards against the class even when
    aggregation is disabled.
  \item Publish a security-property summary in the server's
    deployment documentation: what the chunked-TE handling
    guarantees, what is on the operator, what is on the
    application.
\end{enumerate}

\subsection{For application developers}
\label{sec:rec-app}

\begin{enumerate}
  \item Deploy behind nginx or Apache httpd with default
    \fname{proxy\_request\_buffering on} / \fname{ProxyIOBufferSize}.
    This single configuration choice mitigates the class for the
    upstream regardless of language ecosystem.
  \item If the deployment cannot use such a frontend (single-node
    HAProxy, direct-exposed app server, kubernetes ingress without
    body buffering), write or import a middleware that counts
    chunks per request and short-circuits with HTTP 413 or 408
    beyond a threshold.
  \item Set a body-byte cap (\fname{Content-Length} ceiling,
    framework body-size limit) sized to your application's actual
    needs.
  \item Monitor per-request CPU. Alert on outliers exceeding
    \(2\sigma\) of normal. The amplification produces clear
    per-request CPU spikes that show up in any reasonable
    request-level CPU-accounting metric.
\end{enumerate}

\subsection{For operators}
\label{sec:rec-op}

\begin{enumerate}
  \item Audit the deployment: which servers are direct-exposed,
    which are behind nginx / Apache / HAProxy / a CDN. Categorize
    by Section~\ref{sec:mit-summary} mitigation tier.
  \item For HAProxy-fronted services and direct-exposed services,
    enable per-IP packet-rate limiting at the L4 layer
    (\fname{nftables}, BPF). Set thresholds that catch slow-drip
    without blocking legitimate slow uploaders.
  \item For DDoS-protection vendors (Cloudflare, Akamai, Fastly):
    request explicit confirmation in writing of whether chunked-TE
    bodies are aggregated before forwarding to origin. The
    public documentation is silent on this for most providers.
  \item Set up an alert on per-process CPU breaching some
    threshold for sustained time (e.g., one core saturated for
    \(\geq 30\) seconds attributable to one connection). The
    attack pattern is easy to spot in a process tree but invisible
    in default access logs.
\end{enumerate}

\subsection{For protocol designers}
\label{sec:rec-spec}

\begin{enumerate}
  \item Update RFC 9112 or its successor with non-normative
    guidance on per-chunk delivery granularity, explicitly
    blessing aggregation as spec-compliant. The current spec's
    silence has resulted in fifteen years of independent
    implementations all making the wrong default choice.
  \item Standardize a chunk-count rate-limit negotiation
    primitive at the protocol level (analogous to HTTP/2's
    \fname{SETTINGS\_MAX\_HEADER\_LIST\_SIZE}). A client could
    advertise "I will send at most $N$ chunks", and the server
    could refuse connections that exceed it.
  \item For HTTP/3 over QUIC, consider whether stream-level pacing
    requirements can be tightened to make the same attack class
    structurally impossible (QUIC streams have receiver-side
    flow control but no chunk-count cap).
\end{enumerate}
