\subsection{Limitations}
\label{sec:future-limit}

\paragraph{Network conditions.}
Mode A (bridge-coalesced) and Mode B (paced \SI{100}{\micro\second})
bound the realistic spectrum but do not cover every deployment.
Particularly: cloud LB-to-pod paths sometimes apply per-flow
shapers that approximate Mode B even without an explicit attacker
pacing strategy. We have not measured those configurations
directly.

\paragraph{Single-CPU constraint.}
Every server runs in a \texttt{--cpus=1} container. This is the
single-CPU worst case. Multi-CPU servers fan out work across cores,
but the per-connection cost is still serial per the affected
worker, so multi-CPU does not change the per-connection ratio --
it changes how many concurrent attackers are needed to saturate
the deployment.

\paragraph{TLS overhead not measured.}
Every test is plain HTTP. TLS adds AEAD framing on top of TCP;
TLS records buffer multiple bytes by their nature, which could
incidentally aggregate chunked-TE chunks at the record boundary.
We have not measured the magnitude.

\paragraph{HTTP/3 not measured.}
The Wave 3 set extends the survey to HTTP/2 DATA frames and
WebSocket text frames (Sections~\ref{sec:pf-h2}--\ref{sec:pf-ws}),
but HTTP/3 over QUIC streams is not yet measured. HTTP/3's framing
is similar to HTTP/2's DATA frames, so we expect the per-frame
amplification class to transfer, but QUIC's separate flow-control
and stream model could change the constant or the mitigation
surface; we have not measured it.

\paragraph{Cold start vs warm path.}
JVM tests in particular include some JIT warm-up cost in the
first few requests. We report the warm-path numbers (request
2--N of each cell); cold-path measurements would change the
absolute timings but not the asymptotic shape.

\paragraph{Production traffic distribution.}
The probability that real-world traffic includes per-chunk
amplification attempts is unmeasured. We have not deployed
honeypots or instrumented production servers.

\subsection{Threats to validity}
\label{sec:threats}

We report the measurement-construct limitations explicitly; each
notes the likely \emph{direction} of bias.

\paragraph{Single run per cell (no confidence intervals).}
Nearly every cell is $n{=}1$; we have no within-cell variance and
report no confidence intervals. We therefore make no fine-grained
ranking claims between servers whose per-chunk costs are within a
small factor of each other. The order-of-magnitude separations we
rely on (e.g.\ \fwid{nginx} $\sim\!100\times$ \fwid{uvicorn}; the
Node quadratic vs.\ the linear pack) are robust to plausible
run-to-run noise; sub-factor-of-two differences are not.

\paragraph{CPU sampled via \fname{docker stats} snapshot.}
Where we have CPU at all (64 of 203 cells), it is a single
\fname{docker stats --no-stream} reading times the run duration,
not an integral of \fname{cpuacct.usage}/\fname{cpu.stat}. This is
noisier than integrating cgroup counters, can exceed
\SI{100}{\percent} on a single pinned core, and degrades under
host contention. We treat CPU figures as accurate to roughly the
tens-of-percent level. A re-run should integrate \fname{cpu.stat}
\texttt{usage\_usec} deltas instead.

\paragraph{Wall time used where CPU is absent.}
For the 139 CPU-less cells we report wall-derived per-chunk cost
(Section~\ref{sec:method-metric}). On a saturated single-vCPU
container wall $\approx$ CPU; otherwise wall \emph{over-counts}
CPU by absorbing idle, network, and prober time. Direction of
bias: wall $\geq$ CPU, so wall-derived numbers are upper bounds on
server CPU. The quadratic headline figures (Node 282\,s) are wall
on a fully-pinned, saturated core, and should be read as
``single-core wall, $\approx$ CPU because saturated,'' not as
independently measured CPU integrals.

\paragraph{Single co-located host; prober/SUT contention.}
Prober and server run on one host. Mode~B's prober busy-waits
(\SI{100}{\micro\second} CPU spin per chunk) on the same machine
as the 1-vCPU server-under-test; if they share a core, prober
spin steals cycles and \emph{inflates} server wall time. Direction
of bias: server wall time biased upward.

\paragraph{CFS quota vs.\ dedicated core.}
\texttt{--cpus=1} imposes a CFS bandwidth quota (\SI{100}{\milli\second}
period), not a dedicated physical core (\texttt{--cpuset-cpus}).
Under quota a CPU-bound run is throttled at period boundaries,
adding wall time that is not server work. Direction of bias:
inflates Mode~B wall (and wall-derived per-chunk cost) relative to
a dedicated core; CPU-percentage figures are less affected.

\paragraph{Version pinning and host metadata gaps.}
Several rows omit the exact runtime/version, and the published
dataset does not populate host CPU/kernel metadata, so cross-host
reproducibility is not fully specified. Direction of bias: none on
relative results, but absolute microsecond figures are
host-specific and not portable.

\subsection{Future work}
\label{sec:future-work}

\paragraph{HTTP/3, gRPC, and HTTP/2 stream multiplexing.}
Wave 3 has measured HTTP/2 multiplexed DATA frames and WebSocket
per-frame amplification (Sections~\ref{sec:pf-h2}--\ref{sec:pf-ws});
every HTTP/2 server inherits the per-frame tax, and 4 of 6
WebSocket servers batch correctly. Remaining for future work are
HTTP/3 over QUIC streams and gRPC streaming. A separate, important
gap is the \emph{multiplexed} HTTP/2 attack: our harness sends one
stream per connection, but a single connection can carry the
maximum concurrent stream count, each stream feeding the same
per-frame parser. We expect this to multiply the per-connection
cost by the stream-concurrency limit and to defeat per-IP
connection caps; quantifying it is the most consequential
measurement we have not yet run.

\paragraph{Multipart per-part amplification.}
\fwid{multipart/form-data} is structurally similar: each part has
a header section delivered to the parser callbacks per chunk.
Companion work in
\texttt{findings/starlette/2026-05/STARLETTE\_FORMPARSER\_QUADRATIC/}
(retracted as a security finding after patch verification but the
underlying parser shape is the same) suggests the class transfers.

\paragraph{Production telemetry.}
We have no data on what fraction of production HTTP traffic
includes chunked-TE bodies with small chunks. A honeypot study or
a partnership with a high-traffic CDN would let us estimate the
real-world prevalence of the attack pattern.

\paragraph{Frontend buffering measurement at CDNs.}
Cloudflare, Fastly, Akamai, AWS ALB, and GCP HTTP(S) LB each have
proprietary chunked-body handling. None publicly document whether
they aggregate before forwarding to origin. A measurement campaign
across these would significantly improve the operational
recommendation in Section~\ref{sec:mit-summary}.

\paragraph{Formal model of batching correctness.}
We have argued informally (Section~\ref{sec:rc-spec}) that
batching is spec-compliant under RFC 9112 and ASGI / WSGI /
Servlet. A formal model -- expressed in TLA+ or a similar
specification language -- would make the argument bulletproof
and would let server maintainers verify their own batching
implementations.

\paragraph{Detection signatures.}
Building an open-source IDS / WAF signature for the attack
pattern is straightforward (Section~\ref{sec:tm-detect}) but
requires balancing false positives against attacker evasion.
A reference Snort / Suricata rule set, validated on our
reproducer harness, would be a useful publishable artifact.
