We measured 27 production HTTP/1.1 servers across 7 language
ecosystems plus three C servers -- and, in Wave 3, a further 6
HTTP/2 and 6 WebSocket servers (39 records total) -- for their
handling of the RFC-compliant pathological input "$N$-byte body
delivered as $N$ one-byte chunked-TE chunks." Among the HTTP/1.1
servers, one (Microsoft's Kestrel via \fname{System.IO.Pipelines})
structurally defeats the per-chunk amplification class; 23 are
linear-but-vulnerable with per-chunk costs spanning a factor of
$\sim 65\times$; 3 (Node's built-in \fwid{http.Server},
\fwid{express}, and \fwid{fastify}, which share one substrate)
exhibit superlinear $\Theta(N^2)$ scaling that pins a single CPU
core for minutes per \SI{1.5}{\mebi\byte} of attacker traffic.
(Elixir's \fwid{bandit} is a high-constant linear case,
$\sim$\SI{138}{\micro\second}/chunk with measured exponent
$\sim 1.05$, not quadratic.)

The root cause is a parser/dispatcher boundary design choice, not
a spec violation. RFC 9112 fixes the wire format but is silent on
application-API granularity; ASGI, WSGI, Servlet, and Node's
\fname{Readable} all permit coalescing. The cost of \emph{not}
coalescing is a per-chunk dispatch event whose constant varies by
runtime: ASGI receive, goroutine wake, future poll,
\fname{process.nextTick}, mailbox enqueue, fiber switch, thread
context switch. The amplification class is not unique to any
single runtime; we observe it in every concurrency model we
measure.

The "deploy behind nginx" mitigation widely advised in framework
documentation is valid for nginx and Apache httpd
(\fname{proxy\_request\_buffering on} / \fname{ProxyIOBufferSize}
default), but is \emph{not} valid for HAProxy, which streams the
body upstream by default. Direct-exposed application servers,
HAProxy-fronted deployments, and any deployment with proxy
buffering disabled inherit the full per-chunk cost.

We argue that opt-in batching primitives modeled on Kestrel's
Pipelines pump should be exposed by every event-loop HTTP server,
and that the operational advice "deploy behind nginx" deserves
clearer documentation of its applicability and its limits.

The reproducer harness, raw measurements, and figure-rendering
scripts are published with this paper at
\url{https://github.com/mjbommar/chunkloris-paper}. Anyone with
Docker plus \fname{uv} plus \fname{pdflatex} can reproduce every
number in this paper from the supplied harness.
